Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-11 paper/paper.tex
more stuff

\subsection{The hippocampus: memory, space, and experience replay}
The DMN midline is probably in constant communication
with the HC in the medial temporal lobe \citep{vincet2006}.
The HC is long known to be involved in
memory operations and spatial navigation in animals and humans.

While the HC
is traditionally believed to allow remembering the past,
there is now increasing evidence for a role
in constructing mental models in general
\citep{maguire2016, schacter2007remembering, gelbard2008internally, Javadi2017}.
Its highly recursive anatomical architecture
may be specifically designed to allow reconstructing
entire episodes of experience from memory fragments.
Indeed,
hippocampal damage is
not only associated with an impairment in reexperiencing the past (i.e., amnesia),
but also thinking about one's own future and
imagining new fictitious experiences more broadly \citep{hassabis2007patients}.
Mental scenes created by hippocampus-lesioned patients exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal hippocampus revealed
some constantly active neuronal ensembles whose firing coincided with
distinct locations in space during environmental navigation.
London taxi drivers, individuals with high performance in spatial navigation,
were shown to exhibit increased gray-matter volume in the
hippocampus \citep{maguire2000navigation}.
Indeed, place-specific neuronal populations in the hippocampus
spike one after another when an animal is choosing between alternative
paths \citep{johnson2007neural}.
These neuronal patterns appear to also indicate upcoming behavior
\citep{pfeiffer2013hippocampal}.

But encoding and generative reconstruction in the hippocampus extends
beyond mere spatial knowledge of the environment.
Based on large-scale recordings of hippocampal neuronal populations,
complex spiking patterns can be followed across extended periods including
their modification of input-free self-generated patterns
after environmental events \citep{buzsaki2004large}.
Specific spiking sequences, that were elicited in experimental task conditions,
have been shown to be reenacted spontaneously during
quiet wakefulness and sleep \citep{hartley2014space, o2010play}.
Moreover, spike sequences measured in hippocampal place cells of rats
featured re-occurrence directly after experimental trials
as well as directly before upcoming experimental trials \citep{diba2007forward}.
Such hippocampal ensembles burt during rest and sleep
have been proposed to be critical in communicating local information
to the neocortex for long-term storage, potentially also in the nodes of the DMN.
These hippocampus-subserved mechanisms
probably contribute to
recollecting autobiographical memory episodes, as well as
reexperiencing or newly generating mental scenarios
\citep{hassabis2007patients}.

>>>>

\subsection{The hippocampus: memory, space, and experience replay}
The DMN midline is probably closely linked
with the HC in the medial temporal lobe \citep{vincet2006}.
The HC is long known to be involved in
memory operations and spatial navigation in animals and humans.

While the HC
is traditionally believed to allow remembering the past,
there is now increasing evidence for a role
in constructing mental models in general
\citep{maguire2016, schacter2007remembering, gelbard2008internally, Javadi2017}.
Its recursive anatomical architecture
may be specifically designed to allow reconstructing
entire episodes of experience from memory fragments.
Indeed,
hippocampal damage is
not only associated with an impairment in reexperiencing the past (i.e., amnesia),
but also thinking about one's own future and
imagining new fictitious experiences more broadly \citep{hassabis2007patients}.
Mental scenes created by HC-lesioned patients exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal HC revealed
some constantly active neuronal ensembles whose firing coincided with
distinct locations in space during environmental navigation.
London taxi drivers, individuals with high performance in spatial navigation,
were shown to exhibit increased gray-matter volume in the
HC \citep{maguire2000navigation}.
Indeed, place-specific neuronal populations in the HC
spike one after another when an animal is choosing between alternative
paths \citep{johnson2007neural}.
These neuronal patterns appear to also indicate upcoming behavior
\citep{pfeiffer2013hippocampal}.

But encoding and generative reconstruction in the HC extends
beyond mere spatial knowledge of the environment.
Based on large-scale recordings of hippocampal neuronal populations,
complex spiking patterns can be followed across extended periods including
their modification of input-free self-generated patterns
after environmental events \citep{buzsaki2004large}.
Specific spiking sequences, that were elicited in experimental task conditions,
have been shown to be reenacted spontaneously during
quiet wakefulness and sleep \citep{hartley2014space, o2010play}.
Moreover, spike sequences measured in hippocampal place cells of rats
featured re-occurrence directly after experimental trials
as well as directly before upcoming experimental trials \citep{diba2007forward}.
Such hippocampal ensembles burt during rest and sleep
have been proposed to be critical in communicating local information
to the neocortex for long-term storage, potentially also in the nodes of the DMN.
These HC-subserved mechanisms
probably contribute to
recollecting autobiographical memory episodes, as well as
reexperiencing or newly generating mental scenarios
\citep{hassabis2007patients}.
